Comparing the Effectiveness of the Choropleth Map with a Hexagon Tile Map for Communicating Cancer Statistics

### 2020-01-11 paper/paper.Rmd
choice plot better dims

```{r choices, fig.cap = "Each facet is associated with one lineup, the height of the points show the proportion of the participants that made each choice when considering each lineup. The points coloured orange show the map which contained a trend model, these are the correct choices. The numbers differentiate the replicates of each trend model and type of map display. Participants were able to select 0 to indicate they did not want to choose a map."}
d %>% 
  count(type, trend, choice, replicate, choice, detect_f) %>% 
  group_by(type, trend, replicate) %>% 
  mutate(prop = n/sum(n)) %>% 
  mutate(repl = paste("Rep:", replicate, ":\n", type,  sep = "")) %>%
  mutate(bottom = 0) %>% 
  ggplot() + 
  geom_point(aes(x = choice, y = prop, color = detect_f), size = 4) + 
  geom_segment(aes(x = choice, xend = choice,y = bottom, yend = prop, colour = detect_f), size = 1) +
  facet_grid(repl ~ trend, 
    drop = TRUE, as.table = TRUE, scales = "free_y") +
  labs(x = "Choice of plot in lineup", y = "Amount of choices") +
  scale_colour_manual(values = detect_colours) +
  scale_x_continuous(breaks = seq(from = 0, to = 12)) +
  scale_y_continuous(breaks = seq(from = 0.0, to = 1.0, by = 0.1)) +
  theme(legend.position = "bottom") + 
  guides(colour = FALSE, fill = FALSE) +
  theme(strip.text.y = element_text(angle = 0))
```

>>>>

```{r choices, fig.cap = "Each facet is associated with one lineup, the height of the points show the proportion of the participants that made each choice when considering each lineup. The points coloured orange show the map which contained a trend model, these are the correct choices. The numbers differentiate the replicates of each trend model and type of map display. Participants were able to select 0 to indicate they did not want to choose a map.", fig.height = 8, fig.width =6}
d %>% 
  count(type, trend, choice, replicate, choice, detect_f) %>% 
  group_by(type, trend, replicate) %>% 
  mutate(prop = n/sum(n)) %>% 
  mutate(repl = paste("Rep:", replicate, ":\n", type,  sep = "")) %>%
  mutate(bottom = 0) %>% 
  ggplot() + 
  geom_point(aes(x = choice, y = prop, color = detect_f), size = 3) + 
  geom_segment(aes(x = choice, xend = choice,y = bottom, yend = prop, colour = detect_f), size = 1) +
  facet_grid(repl ~ trend, 
    drop = TRUE, as.table = TRUE, scales = "free_y") +
  labs(x = "Choice of plot in lineup", y = "Amount of choices") +
  scale_colour_manual(values = detect_colours) +
  scale_x_continuous(breaks = seq(from = 0, to = 12)) +
  scale_y_continuous(breaks = seq(from = 0.0, to = 1.0, by = 0.1)) +
  theme(legend.position = "bottom") + 
  guides(colour = FALSE, fill = FALSE) +
  theme(strip.text.y = element_text(angle = 0))
```
